\textls[-0]{\thetitle}

### 2023-03-05 syn-translate.tex
Change makefile

The implementation described in \cref{sec:coqimpl} can be formalized in
our metatheory. The described compilation strategy can be considered as
a \textit{syntactic translation}, a function mapping from our syntactic
(QIIT-)model to a ``subpart''\footnote{Not exactly subpart---the only
difference lies in "Wrec". In our metatheory, it is constructed
using linkage; in ``subpart'', it will be using $\Sigma$-types (translation
of the linkage).} of our syntactic (QIIT-)model \textit{without
linkages}.\footnote{Here, syntactic QIIT-model can be roughly understood
as just AST, with equational rules acting like quotient. So this mapping
is mapping AST to AST, respecting quotient/judgemental equality.} This
``subpart'' is the standard MLTT with inductive type signatures, an
(unconventional) formulation of W-types,
and recursors that use $\Sigma$-types to aggregate handlers.

@@

We use $\denotesT{}$ as the translation. This translation behaves like identity\YZ{What does "invariant" mean?}\EDJreply{behaves like identity. Sorry I should have said "subpart is invariant under this translation" instead}
under the subpart. Since we are in an intrinsic setting, everything here
is well-typed (well-formed)including this translation. Thus
$\denotesT{T}$ means the same as $\denotesT{\goodType{\Gamma}{T}{}}$
(i.e. every type is tracking its context). In other words, every
derivation of any judgement will track its ``context''. This will be
clearer in the (pseudo-)Agda formalization.

>>>>

The implementation described in \cref{sec:coqimpl} has hinted the fact that
linkage can be translated into dependent tuple type.
The described compilation strategy can be considered as
a \textit{type preserving syntactic translation}, a function mapping from our syntactic
model to a ``subpart''\footnote{Not exactly subpart---the only
difference lies in "Wrec". In our metatheory, it is constructed
using linkage; in ``subpart'', it will be using $\Sigma$-types (translation
of the linkage).} of our syntactic model \textit{without
linkages}.

This ``subpart'' is the standard MLTT with an
(unconventional) formulation of W-types,
and recursors that use $\Sigma$-types to aggregate handlers.

@@

We use $\denotesT{}$ as the translation. This translation behaves like identity
\YZ{What does "invariant" mean?}\EDJreply{behaves like identity. Sorry I should have said "subpart is invariant under this translation" instead}
under the subpart. Since we are in an intrinsic setting, everything here
is well-typed (well-formed)including this translation. Thus
$\denotesT{T}$ means the same as $\denotesT{\goodType{\Gamma}{T}{}}$
(i.e. every type is tracking its context). In other words, every
derivation of any judgement will track its ``context''.
